Extended Data

### 2021-10-21 doc/manuscript/Dow_manuscript_Nature.Rmd
author contributions
@camerondow35 , this doesn't need to be super specific. I condensed into a typical list.

All authors gave suggestions on improvements to manuscript during development.

Albert Y. Kim - Developed and assisted in coding the statistical framework for analyses used.

Loïc D’Orangeville - Provided tree core chronologies for additional sites, gave feedback on draft of manuscript.

Erika B. Gonzalez-Akre - Oversees and manages data collection at SCBI.

Ryan Helcoski - Collected and measured cores at SCBI.

Valentine Herrmann - Assisted with coding and interpretation of statistical results.

Grant L. Harley - Provided tree core chronologies for additional sites and assisted with interpretation of results.

Justin T. Maxwell - Provided tree core chronologies for additional sites, detrended crns, and assisted with interpretation of results.

Ian R. McGregor - Assisted with the acquisition and processing of leaf phenology data.

William McShea -

Sean McMahon - Provided R functions for dealing with dendroband data (RDendrom)

David A. Orwig -

Neil Pederson - Provided tree core chronologies for additional sites and gave feedback on tree core analysis

Alan J. Tepley -

Kristina J. Anderson-Teixeira - Oversaw all aspects of research and manuscript development.

>>>>

Cameron Dow and Kristina J. Anderson-Teixeira conceived the ideas and designed the study; 
Cameron Dow, Loïc D’Orangeville, Erika B. Gonzalez-Akre, Ryan Helcoski, Grant L. Harley, Justin T. Maxwell, Ian R. McGregor, William McShea, David A. Orwig, Neil Pederson, Alan J. Tepley, and Kristina J. Anderson-Teixeira collected or oversaw collection of data; 
Cameron Dow, Albert Y. Kim, Valentine Herrmann, Justin T. Maxwell, Ian R. McGregor, Sean McMahon analyzed the data or provided analytical tools; 
Cameron Dow and Kristina J. Anderson-Teixeira led the writing of the manuscript. 
All authors contributed critically to the drafts and gave final approval for publication.
